---
title: "output_03132020_11"
author: "Young-Kyung Kim"
date: "3/13/2021"
output: pdf_document
---
```{r, echo=FALSE}

library(dplyr)
library(pwr)
library(stringr)

df <- read.csv(file="Master_Coding_CSV_03132020_19.csv", header=TRUE, sep=',', stringsAsFactors = FALSE)
#detect whether something has two languages of similar prominence
#set all null values to numbers so that the if-else doesn't fail early 
df$kor_hier <- strtoi(ifelse(df$kor_hier == FALSE, 100, df$kor_hier))
df$eng_hier <- strtoi(ifelse(df$eng_hier == FALSE, 200, df$eng_hier))
df$other_hier <- strtoi(ifelse(df$other_hier == FALSE, 300, df$other_hier))
#how big is the biggest text on a sign?
df$prom_size <- pmin(df$kor_hier, df$eng_hier, df$other_hier)
#this is just a check for now; shouldn't be a problem after I fix the dataset. For now, exclude these rows.
df$prom_lang_matched <- ifelse(df$eng_hier == df$kor_hier, FALSE, ifelse(df$kor_hier == df$other_hier, FALSE, ifelse(df$other_hier == df$eng_hier, FALSE, TRUE)))
#if there are 2+ scripts, which script is more prominent?
df$prom_lang <- ifelse(df$prom_size > 50, NA, (ifelse(df$kor_hier == df$prom_size, 'han', ifelse(df$eng_hier == df$prom_size, 'roman', 'other'))))
#set the right ones to factor variables
df[c("type_loan", "type_loan_2", "type_loan_3")] <- lapply(df[c("type_loan", "type_loan_2", "type_loan_3")], as.factor)

#levels(df$type_loan) <- c("1", "2", "3", "4", "5")
#levels(df$type_loan_2) <- c("1", "2", "3", "4", "5")
#levels(df$type_loan_3) <- c("1", "2", "3", "4", "5")
df$total_loanwords <- sum(df$no_loan, df$no_loan_2, df$no_loan_3)
df$total_loan_2 <- 
#if there is one script, which one is it? factor variables 
df$lang <- ifelse(df$prom_size > 50, 
                  ifelse(df$kor_check == 1, 1, 
                  ifelse(df$eng_check == 1, 2, 
                  ifelse(!is.na(df$chinese), 3, 
                  ifelse(!is.na(df$japanese), 4,
                  ifelse(!is.na(df$span), 5,
                  ifelse(!is.na(df$fren), 6, 
                  ifelse(!is.na(df$arabic), 7, 
                  ifelse(!is.na(df$viet), 8,
                  ifelse(!is.na(df$thai), 9,
                  ifelse(!is.na(df$turkish), 10, -9)))))))))),NA)
#assign binary location variable
df$location <- ifelse(df$point_id < 58, 1, 0)
#remove rows where prominence is matched between two scripts 
df <- df[df$prom_lang_matched == TRUE,]
#create df for calculating relative area 
df['prom_lang_matched'] <- NULL
df_area <- df
#c("How many different sites?", length(unique(df$site_id)))
#c("How many different points?", length(unique(df$point_id)))
```

```{r, echo=FALSE}
#prepping sign and size df
for (i in unique(df$site_id)) {
  same_site <- df$site_id == i
  same_sign <- (df$sign_id == df$sign_id) & (same_site)
  same_sign <- ifelse(is.na(same_sign), FALSE, same_sign)
  #number of true
  p = df[same_sign==TRUE, ]
  same_sign[strtoi(rownames(p)[which.min(p$prom_size)])] = FALSE
  if (length(which(same_sign)) == 0) next
  df = df[-c(which(same_sign)),]
}
#create df for calculating signs
df_sign <- df
```

# SCRIPTS BY SIGN
## Counts and proportions of dominant scripts across Itaewon and Koreatown.
Dominant scripts include all single-script signs of each language
```{r, echo=FALSE}
# Total signs in each location
total_signs <- nrow(df_sign)
koreatown_signs <- df_sign[df_sign$location == 0, ]
itaewon_signs <- df_sign[df_sign$location == 1, ]
koreatown_total <- nrow(koreatown_signs)
itaewon_total <- nrow(itaewon_signs)

# Proportions of dominant scripts in each location 
koreatown_hangeul_prom <- sum(koreatown_signs$prom_lang == 'han', na.rm=TRUE)
koreatown_hangeul_ss <- sum(koreatown_signs$lang == 1, na.rm=TRUE)
koreatown_hangeul_all <- koreatown_hangeul_prom + koreatown_hangeul_ss
koreatown_english_prom <- sum(koreatown_signs$prom_lang == 'roman', na.rm=TRUE)
koreatown_english_ss <- sum(koreatown_signs$lang == 2, na.rm=TRUE)
koreatown_english_all <- koreatown_english_prom + koreatown_english_ss
koreatown_other_prom <- sum(koreatown_signs$prom_lang == 'other', na.rm=TRUE)
koreatown_other_ss <- sum(((koreatown_signs$lang != 2) & (koreatown_signs$lang != 1)), na.rm=TRUE)
koreatown_other_all <- koreatown_other_prom + koreatown_other_ss
#confused don't think that this is particularly meaningful--it's the total of signs that don't have a prominent language--they are single script
#koreatown_mixed_prom <- sum(!is.na(koreatown_signs$prom_lang), na.rm=TRUE)

itaewon_hangeul_prom <- sum(itaewon_signs$prom_lang == 'han', na.rm=TRUE)
itaewon_hangeul_ss <- sum(itaewon_signs$lang == 1, na.rm=TRUE)
itaewon_hangeul_all <- itaewon_hangeul_prom + itaewon_hangeul_ss
itaewon_english_prom <- sum(itaewon_signs$prom_lang == 'roman', na.rm=TRUE)
itaewon_english_ss <- sum(itaewon_signs$lang == 2, na.rm=TRUE)
itaewon_english_all <- itaewon_english_prom + itaewon_english_ss
itaewon_other_prom <- sum(itaewon_signs$prom_lang == 'other', na.rm=TRUE)
itaewon_other_ss <- sum(((itaewon_signs$lang != 2) & (itaewon_signs$lang != 1)), na.rm=TRUE)
itaewon_other_all <- itaewon_other_prom + itaewon_other_ss
#see above
#itaewon_mixed_prom <- sum(!is.na(itaewon_signs$prom_lang), na.rm=TRUE)

koreatown_prom_sum <- sum(koreatown_hangeul_prom, koreatown_english_prom, koreatown_other_prom)
koreatown_all_sum <- sum(koreatown_hangeul_all, koreatown_english_all, koreatown_other_all)
itaewon_prom_sum <- sum(itaewon_hangeul_prom, itaewon_english_prom, itaewon_other_prom)
itaewon_all_sum <- sum(itaewon_hangeul_all, itaewon_english_all, itaewon_other_all)

dominant_scripts <- data.frame(c(koreatown_hangeul_all, itaewon_hangeul_all, sum(koreatown_hangeul_all, itaewon_hangeul_all)), 
                         c(koreatown_hangeul_all/koreatown_total, itaewon_hangeul_all/itaewon_total, sum(koreatown_hangeul_all, itaewon_hangeul_all)/total_signs),
                         c(koreatown_english_all, itaewon_english_all, sum(koreatown_english_all, itaewon_english_all)), 
                         c(koreatown_english_all/koreatown_total, itaewon_english_all/itaewon_total, sum(koreatown_english_all, itaewon_english_all)/total_signs),
                         c(koreatown_other_all, itaewon_other_all, sum(koreatown_other_all, itaewon_other_all)), 
                         c(koreatown_other_all/koreatown_total, itaewon_other_all/itaewon_total, sum(koreatown_other_all, itaewon_other_all)/total_signs), 
                         c(koreatown_all_sum, itaewon_all_sum, sum(koreatown_all_sum, itaewon_all_sum)),
                         c(koreatown_all_sum/koreatown_total, itaewon_all_sum/itaewon_total, sum(koreatown_all_sum, itaewon_all_sum)/total_signs),
                         c(koreatown_total, itaewon_total, total_signs))

names(dominant_scripts) <- c('Hangeul_count', 'Hangeul_prop', 'English_count', 'English_prop', 'Other_count', 'Other_prop', 'Total Coded', 'Total Coded_prop', 'Total')
rownames(dominant_scripts) <- c("Koreatown", "Itaewon", "Both")
dominant_scripts
```

## Test for differences in proportions of dominant scripts in Itaewon and Koreatown 
### Hangeul
```{r, echo=FALSE}
#power test 
pwr.2p2n.test(n1=koreatown_total, n2=itaewon_total, sig.level=0.05, power=.8)

#test for proportions of Korean
t.test(c(rep(1, koreatown_hangeul_all), rep(0, (koreatown_total - koreatown_hangeul_all))), c(rep(1, itaewon_hangeul_all), rep(0, (itaewon_total - itaewon_hangeul_all))))
```

### English
```{r, echo=FALSE}
#test for proportions of dominant Roman script
t.test(c(rep(1, koreatown_english_all), rep(0, (koreatown_total - koreatown_english_all))), c(rep(1, itaewon_hangeul_all), rep(0, (itaewon_total - itaewon_hangeul_all))))
```

## Counts and proportions of languages in single-script signs
These do not include signs where there are more than one script 
```{r, echo=FALSE}
columns <- c('koreatown_signs', 'itaewon_signs', 'df_sign')
columns <- lapply(columns, get)
nm <- c('koreatown_signs', 'itaewon_signs', 'df_sign')

for (i in 1:3) {
  d <- (data.frame(unlist(table(columns[[i]]['lang'], useNA="ifany"))))
  n <- d$Var1
  d <- t(data.frame(d[,-1]))
  colnames(d) <- n
  print(c(nm[i]))
  print(d)
}
#full_join(t(table(koreatown_signs$lang)), t(prop.table(table(koreatown_signs$lang))), t(table(itaewon_signs$lang)), t(prop.table(table(itaewon_signs$lang))), t(table(df_sign$lang)), t(prop.table(table(df_sign$lang))))
```

## Counts and proportions of languages in single-script signs
These do not include signs where there are more than one script 
```{r}
k_check <- koreatown_signs
sapply()
```

## Test for differences in proportions of single-script signs in Itaewon and Koreatown 
```{r, echo=FALSE}
# power test
pwr.2p2n.test(n1=sum(!is.na(koreatown_signs$lang), na.rm = TRUE), n2=sum(!is.na(itaewon_signs$lang), na.rm = TRUE), sig.level=0.05, power=0.8)

# t test
t.test()
```

## SCRIPTS BY AREA
```{r, echo=FALSE}
# it makes sense to do loanword shit with the area table since no rows have been deleted 
koreatown_area <- df_area[df_area$location == 0, ]
itaewon_area <- df_area[df_area$location == 1, ]

koreatown_english_loanwords <- sum(c(koreatown_area$no_loan, koreatown_area$no_loan_2, koreatown_area$no_loan_3), na.rm=TRUE)
itaewon_english_loanwords <- sum(c(itaewon_area$no_loan, itaewon_area$no_loan_2, itaewon_area$no_loan_3), na.rm=TRUE)
total_english_loanwords <- sum(c(df_area$no_loan, df_area$no_loan_2, df_area$no_loan_3), na.rm=TRUE)
total_words <- sum(df_area$total_words)

#create a table that contains all the summaries we need 
koreatown_area[c("point_id", "sign_id", "site_description", "location")] <- NULL
itaewon_area[c("point_id", "sign_id", "site_description", "location")] <- NULL
#d <- koreatown_signs %>% count(type_loan)
#f <- itaewon_signs %>% count(type_loan)
#e <- t(summary(koreatown_signs$type_loan))
```

## LOANWORDS
```{r, echo=FALSE}
k <- aggregate(koreatown_area$no_loan, by=list(Category=koreatown_area$type_loan), FUN=sum)
k2 <- aggregate(koreatown_area$no_loan_2, by=list(Category=koreatown_area$type_loan_2), FUN=sum)
i <- aggregate(itaewon_area$no_loan, by=list(Category=itaewon_area$type_loan), FUN=sum)
i2 <- aggregate(itaewon_area$no_loan_2, by=list(Category=itaewon_area$type_loan_2), FUN=sum)
d <- aggregate(df_area$no_loan, by=list(Category=df_area$type_loan), FUN=sum)
d2 <- aggregate(df_area$no_loan_2, by=list(Category=df_area$type_loan_2), FUN=sum)
e <- data.frame(factor(c(1, 2, 3, 4, 5)), c(0, 0, 0, 0, 0))
names(e) <- c("Category", "p")

#Basic English loanwords comparison table
english_loanwords <- data.frame(c(koreatown_english_loanwords, itaewon_english_loanwords, total_english_loanwords), c(koreatown_english_loanwords/sum(koreatown_area$total_words, na.rm=TRUE), itaewon_english_loanwords/sum(itaewon_area$total_words, na.rm=TRUE), total_english_loanwords/total_words))
names(english_loanwords) <- c("Total English loanwords", "Proportion of loanwords")
english_loanwords

#power test for the proportion of English loanwords in Koreatown and Itaewon
pwr.2p2n.test(n1=sum(koreatown_area$total_words, na.rm=TRUE), n2=sum(itaewon_area$total_words, na.rm=TRUE), sig.level=0.05, power=.8)

#t-test for the proportion of English loanwords in Koreatown and Itaewon 
t.test(c(rep(1, koreatown_english_loanwords), rep(0, (sum(koreatown_area$total_words, na.rm=TRUE) - koreatown_english_loanwords))), c(rep(1, itaewon_english_loanwords), rep(0, (sum(itaewon_area$total_words, na.rm=TRUE) - itaewon_english_loanwords))))

english_loanwords_table <- full_join(k, e, by="Category")
english_loanwords_table["p"] <- NULL

english_loanwords_table <- full_join(english_loanwords_table, k2, by="Category")
english_loanwords_table$Koreatown_Int <- rowSums(cbind(english_loanwords_table$x.x, english_loanwords_table$x.y), na.rm=TRUE)
english_loanwords_table$Koreatown_Prop <- english_loanwords_table$Koreatown_Int/koreatown_english_loanwords

english_loanwords_table <- full_join(english_loanwords_table, i, by="Category")
english_loanwords_table <- full_join(english_loanwords_table, i2, by="Category")
english_loanwords_table$Itaewon_Int <- rowSums(cbind(english_loanwords_table$x.x.x, english_loanwords_table$x.y.y), na.rm=TRUE)
english_loanwords_table$Itaewon_Prop <- english_loanwords_table$Itaewon_Int/itaewon_english_loanwords

english_loanwords_table <- full_join(english_loanwords_table, d, by="Category")
english_loanwords_table <- full_join(english_loanwords_table, d2, by="Category")
english_loanwords_table$Both_Int <- rowSums(cbind(english_loanwords_table$x.x.x.x, english_loanwords_table$x.y.y.y), na.rm=TRUE)
english_loanwords_table$Both_Prop <- english_loanwords_table$Both_Int/total_english_loanwords
  
english_loanwords_table <- english_loanwords_table[c("Category", "Koreatown_Int", "Koreatown_Prop", "Itaewon_Int", "Itaewon_Prop", "Both_Int", "Both_Prop")]
english_loanwords_table
```


## Words
### Korean loanwords (Roman script)
```{r, echo=FALSE}
# BASED ON SIGNS 

# BASED ON SIZE 
# parsing for the different loanwords 

loanwords <- df_area$word_loan[!is.na(df_area$word_loan) & (df_area$word_loan != "")]
loanwords_2 <- df_area$words_loan_2[!is.na(df_area$words_loan_2) & (df_area$words_loan_2 != "")]
loanwords_3 <- df_area$words_loan_3[!is.na(df_area$words_loan_3) & (df_area$words_loan_3 != "")]
loanwords <- c(loanwords, loanwords_2, loanwords_3)
loanwords <- unlist(str_split(loanwords, ", "))
unique_loanwords <- unique(loanwords)
unique_loanwords

korean_loanwords <- df_area$kor_loan[(df_area$kor_loan != "")]
korean_loanwords
```

### English loanwords
In Koreatown
```{r, echo=FALSE}
loanwords <- koreatown_area$word_loan[!is.na(koreatown_area$word_loan) & (koreatown_area$word_loan != "")]
loanwords_2 <- koreatown_area$words_loan_2[!is.na(koreatown_area$words_loan_2) & (koreatown_area$words_loan_2 != "")]
loanwords_3 <- koreatown_area$words_loan_3[!is.na(koreatown_area$words_loan_3) & (koreatown_area$words_loan_3 != "")]
loanwords <- c(loanwords, loanwords_2, loanwords_3)
koreatown_loanwords_list <- unlist(str_split(loanwords, ", "))
koreatown_loanwords_list <- unique(koreatown_loanwords_list)
koreatown_loanwords_list
```

In Itaewon
```{r, echo=FALSE}
loanwords <- itaewon_area$word_loan[!is.na(itaewon_area$word_loan) & (itaewon_area$word_loan != "")]
loanwords_2 <- itaewon_area$words_loan_2[!is.na(itaewon_area$words_loan_2) & (itaewon_area$words_loan_2 != "")]
loanwords_3 <- itaewon_area$words_loan_3[!is.na(itaewon_area$words_loan_3) & (itaewon_area$words_loan_3 != "")]
loanwords <- c(loanwords, loanwords_2, loanwords_3)
itaewon_loanwords_list <- unlist(str_split(loanwords, ", "))
itaewon_loanwords_list <- unique(itaewon_loanwords_list)
itaewon_loanwords_list
```

```{r, eval=FALSE}
# THIS IS SOME USELESS ASS CODE
columns <- c('koreatown_area', 'itaewon_area', 'df_area')
columns <- lapply(columns, get)
p <- c(koreatown_english_loanwords, itaewon_english_loanwords, sum(koreatown_english_loanwords, itaewon_english_loanwords))
table <- matrix(, nrow=3*5, ncol=2)
counter = 1
mask <- c(FALSE, TRUE, FALSE, TRUE, FALSE, TRUE, FALSE, TRUE, FALSE, TRUE, FALSE, FALSE)
for (i in 1:length(columns)) {
  #temp <- unlist(summary(columns[[i]]['type_loan']))
  temp <- aggregate((columns[[i]]['no_loan']), by=list(Category=(columns[[i]]['type_loan'])), FUN=sum)
  #temp <- (unlist(str_split(temp, ":")))
  #temp2 <- unlist(summary(columns[[i]]['type_loan_2']))
  #temp2 <- (unlist(str_split(temp, ":")))
  #temp3 <- unlist(summary(columns[[i]]['type_loan_3']))
  #temp3 <- (unlist(str_split(temp, ":")))
  # element wise sum 
  #print(c(temp, temp2, temp3))
  #temp <- strtoi(str_trim(temp[mask])) + strtoi(str_trim(temp2[mask])) + strtoi(str_trim(temp3[mask]))
  #print(temp)
  #table[(((counter-1)*5)+1):(counter*5), 1] <- temp
  #table[(((counter-1)*5)+1):(counter*5), 2] <- temp/p[i]
  #print(table[(((counter-1)*5)+1):(counter*5), ])
  #print(temp)
  #print(temp/p[i])
  counter = counter + 1
}



table <- cbind(koreatown_signs$type_loan, itaewon_signs$type_loan)
mat <- matrix(, nrow = 6, ncol = 4)
mat[, 1] <- summary(koreatown_signs$type_loan)

for(i in 1:2) {
   mat[, i] <- summary(table$i)
}

koreatown_signs
```